%-------------------------
% Resume EN
% Author : Tom FRERET
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{charter}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\setlength{\tabcolsep}{0in}

% Disable hyphenation to prevent word breaks
\hyphenpenalty=5000
\exhyphenpenalty=5000

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \begin{minipage}[t]{\dimexpr\linewidth-2em\relax}
    \textbf{#1}{: #2 \vspace{-2pt}}
    \end{minipage}
  }
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeIndentedLine}[2]{
  \noindent\hspace*{8pt}\parbox[t]{\dimexpr\linewidth-2em\relax}{\textbf{#1}: #2\vspace{2pt}}
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}

\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}


\begin{document}

%--------------------
%     Header
%--------------------
\begin{center}
  \textbf{\Huge Tom Freret} \\ \vspace{3pt}
  \small \faMapMarker* \hspace{2pt}\texttt{France} \hspace{1pt}
  \hspace{1pt} \faEnvelope \hspace{2pt} \href{mailto:first.last@email.com}{first.last@email.com} \hspace{1pt}
  \hspace{1pt} \faPhone \hspace{2pt} +33123456789 \hspace{1pt}
  \hspace{1pt} \faGithub \hspace{2pt} \href{https://github.com/tfreret}{/tfreret} \hspace{1pt}
  \hspace{1pt} \faLinkedinIn \hspace{2pt} \href{https://linkedin.com/tom-freret}{/tom-freret} \hspace{1pt}
  % \hspace{1pt} \faGlobe \hspace{2pt} \href{https://tfreret.fr}{tfreret.fr}
\end{center}


%--------------------
%     Summary
%--------------------
% \small{...}

%--------------------
%     Experience
%--------------------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Orange Wholesale}{Rennes, France}
      {Software Engineer - Apprenticeship}{April 2023 -- Present}
      \resumeItemListStart
        \resumeItem{End-of-Study Project (ongoing, 6 months)}{Led modernization of legacy PHP/Apache services to stateless Kubernetes-based cloud in Golang, collaborating cross-functionally to integrate OpenTelemetry, GitLab CI/CD pipelines, and reusable packages.}
        \resumeItem{AI Code Review}{Designed automated code review system in Python, tailored with prompt engineering to pre-analyze pull requests and reduce review load.}
        \resumeItem{Evita}{Coordinated supervision scenarios across stakeholders for call center with simulated VoIP, SMS alerting, and silent anomaly detection across 6 client journeys.}
        \resumeItem{TracerouteGraph}{Grafana plugins with React and D3.js to visualize traceroute network metrics, now actively used in monitoring, with a clear improvement in network observability.}
        \resumeItem{Cockpit}{Mentored code reviews and improved alerting microservices in Golang by optimizing backends and strengthening automated Docker-based tests. Shared best practices with team.}
      \resumeItemListEnd
    \resumeSubheading
      {Orange Innov}{Bucharest, Romania}
      {Devops Engineer - Internship}{June 2025 -- September 2025}
      \resumeItemListStart
        \resumeItem{Cloud Console}{Refined Java Spring Boot app for managing multi-cloud projects with budget-rights controls. Gathered and implemented user feedback from stakeholders.}
        \resumeItem{Mailing Service}{Led design and deployment of Java Spring Boot mailing service with GitLab CI/CD pipeline and automated deployment on Google Cloud Run.}
    \resumeItemListEnd
        \resumeSubheading
      {Orange Wholesale}{Rennes, France}
      {Full-Stack Developer - Internship}{April 2023 -- July 2023}
      \resumeItemListStart
        \resumeItem{Team247}{Gathered user requirements and delivered PHP/JavaScript web app for validating on-call schedules to improve calendar management. Collected feedback for iterative improvement.}
        \resumeItem{RTB3}{Designed and owned modular test libraries with Robot Framework and Shell scripting to automate SIM card control. Documented processes for team reuse.}
      \resumeItemListEnd
    \resumeSubheading
      {Districenter}{Saint-Aubin-du-Cormier, France}
      {Student Warehouse Worker}{Summers 2019 -- 2021}
      \resumeItemListStart
        \resumeItemPlain{Rehired every summer for reliability and immediate autonomy in a fast-paced warehouse environment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------------------
%     Education
%--------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {IMT Atlantique}{Nantes, France}
      {Engineer's degree (Apprenticeship) - Software Development - GPA: 3.84}{September 2023 -- September 2026}
      \resumeItemListStart
        \resumeItem{Airport IoT System}{Collaborated on distributed system to simulate and monitor airport sensors via MQTT and ESP32 with Golang services and a React dashboard.}
        \resumeItem{Pascal.es}{People's Choice Award for designing a peer-support app against alcoholism with Figma (Hacking Health Nantes / Nantes Design School).}
    \resumeItemListEnd
    \resumeSubheading
      {IUT of Nantes}{Nantes, France}
      {Bachelor's degree in Computer Science}{September 2021 -- September 2023}
      \resumeItemListStart
        \resumeItem{Pixel Runner}{Developed networked multiplayer logic in Golang for a 2D speed game.}
        \resumeItem{Fruits}{E-commerce sites in PHP and Vue.js with cart and online payment management.}
        \resumeItem{Martian Chess}{Kotlin strategy game with advanced design pattern implementation.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%--------------------
%     Skills
%--------------------
\noindent
\begin{minipage}[t]{0.48\textwidth}
\raggedright
\section{Skills}
\small{
\resumeIndentedLine{Development}{Go, Java, TypeScript/JavaScript (React), SQL, PHP, Kotlin, Python}
\resumeIndentedLine{Frameworks/Tools}{Git, Docker, Kubernetes, GitLab CI/CD, Nix, Ansible}
\resumeIndentedLine{Data \& Observability}{OpenTelemetry stack, Grafana, Opensearch, InfluxDB}
\resumeIndentedLine{Methodologies}{Agile, Design Patterns, Agentic AI, SpecDriven Development}
}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\raggedright
\section{Languages \& Interests}
\small{
\resumeIndentedLine{Languages}{French (Native), English (TOEIC 950/C1), German (Basic)}
\resumeIndentedLine{Volunteer}{Multiple Sclerosis Association}
\resumeIndentedLine{Interests}{Cooking, climbing, self-hosting/electronics, running, motorcycling}
}
\end{minipage}

\end{document}